StateSpaceModels.jl: a Julia Package for Time-Series Analysis in a State-Space Framework

### 2019-10-24 paper/paper.tex
Updating paper with new types and diagnostics (#105)
* Updating paper with new types and diagnostics
Add best seed optimization result as an option in verbose (#111)
* added best seed optimization result

* update paper.pdf and paper.tex

In this step, the Kalman filtering, the maximum likelihood estimation of the fixed parameters, and the smoothing are conducted. The optional argument \texttt{verbose}, which defaults to 1, specifies the verbosity: 0 for no output, 1 for some progress information, and 2 for progress information as well as the optimization log.

>>>>

In this step, the Kalman filtering, the maximum likelihood estimation of the fixed parameters, and the smoothing are conducted. The optional argument \texttt{verbose}, which defaults to 1, specifies the verbosity: 0 for no output, 1 for some progress information, 2 for progress information and summary of the optimization result and 3 for progress information as well as the full optimization log.
